Congestion-Aware Join Optimization in Key-Value Stores

### 2014-07-30 paper/paper.tex
Additional paper text

\section{System Architecture}

@@

>>>>

\section{System Overview}

\subsection{Query Model}

\subsection{Architecture}

If we were to use fair share allocation, then the node with the largest share of the query results, bottlenecked by available bandwidth, would become a straggler.
Nodes with a small share of query results could finish much more quickly only to wait for these stragglers.
To minimize the overall completion time of queries, we can allocate bandwidth to each node as the fraction of query results which will be returned by the node.
This will speed up stragglers at the expense of slowing down nodes with a smaller allocation.
However, the net result is a reduction in the average execution cost.

We currently deal with a read-only workload where the distribution of data is known by all nodes.
Each node is able to calculate the fraction of query results it will return.

@@

We also have not dealt with the possibility of updates as well as replication.
There is potential to further exploit SDN techniques by allowing low latency updates to data in the presence of the high bandwidth flows used for query processing.
